% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TeX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,MMMyyyy,nonstop]{simpleresumecv}
% Class options:
% a4paper, letterpapesr, draft, nonstop
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy
\usepackage[utf8]{inputenc}  % assumes input is utf8 encoded
%\usepackage[T1]{fontenc}
%\usepackage[turkish]{babel}
\usepackage{listings}
\usepackage{import} %\nonstopmode
\usepackage{makeidx}
\usepackage{appendix}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage[table]{xcolor}
\usepackage{enumerate}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{hyperref} 
\usepackage{xeCJK}
\usepackage{xunicode}
\usepackage[babelshorthands]{polyglossia}
%\setotherlanguages{turkish}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Islam Mansour}
\newcommand{\CVTitle}{Islam Mansour's CV for the University of Stuttgart}
\newcommand{\CVNote}{CV compiled on {\today} for T\"{U}B\.{I}TAK}
\newcommand{\CVWebpage}{http://web.itu.edu.tr/\textasciitilde mansour/}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{\CVAuthor}

\begin{subtitle}
\href{https://www.google.com.tr/maps/place/ITU+Ucak+ve+Uzay+Bilimleri+Fakultesi/}
{Vadi Yurt, D Blok 225/2, {\.I}T{\"{U}} Ayazaga Campus, Maslak, ISTANBUL 34469, Turkey}
\par
\href{mailto:mansour@itu.edu.tr}
{mansour@itu.edu.tr}
\,\SubBulletSymbol\,
Skype: islam.alam.m
\,\SubBulletSymbol\,
+90\,553\,000\,7301
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\CVWebpage}
\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section
{Education}
{Education}
{PDF:Education}

\href{http://www.itu.edu.tr/en/}
{\textbf{Istanbul Technical University}},
Istanbul, Turkey 

\GapNoBreak
\BulletItem
Bachelor of Science (B.S.) in
\href{http://www.uubf.itu.edu.tr/}
{Astronautical Engineering}
\hfill
\DatestampYMD{2014}{09}{25} --
expected \DatestampYMD{2017}{02}{05}
\begin{detail}
\SubBulletItem
\href{http://www.sis.itu.edu.tr/eng/curriculums/plan/UZBE/201110.html} {Relevant Coursework:} 
\href{http://ssb.sis.itu.edu.tr:9000/pls/PROD/itu_icerik.p_download?file=UZB422E}
{Spacecraft Systems Design,}
\href{http://ssb.sis.itu.edu.tr:9000/pls/PROD/itu_icerik.p_download?file=UCK362E}
{Automatic Control,}
\href{http://ssb.sis.itu.edu.tr:9000/pls/PROD/itu_icerik.p_download?file=UZB421E} 
{Attitude Determination and Control,}
\href{http://ssb.sis.itu.edu.tr:9000/pls/PROD/itu_icerik.p_download?file=UZB352E}
{Orbital Mechanics, }
\href{http://ssb.sis.itu.edu.tr:9000/pls/PROD/itu_icerik.p_download?file=UCK226E} 
{Structural and Mechanical Vibration.}
\SubBulletItem
Honor List.
\SubBulletItem
Cumulative GPA: 3.40 / 4.00
\end{detail}



\BigGap
\href{https://www.vutbr.cz/en/}
{\textbf{Brno University of Technology}},
Brno, Czech Republic

\GapNoBreak
\BulletItem
Erasmus+ Exchange Programme
\href{https://www.fme.vutbr.cz/index.html?lang=1}
{ }
\hfill
\DatestampYMD{2015}{09}{25} --
\DatestampYMD{2016}{02}{05}
\begin{detail}
\SubBulletItem
Cumulative GPA: 3.69 / 4.00
\end{detail}

\BigGap
\href{http://cu.edu.eg/Home}
{\textbf{Cairo University}},
Cairo, Egypt

\GapNoBreak
\BulletItem
\href{http://eng.cu.edu.eg/en/}
Undergraduate Student
(transferred to Istanbul Technical University)
\hfill
\DatestampYMD{2011}{09}{16} --
\DatestampYMD{2014}{06}{28}
\begin{detail}
\SubBulletItem
Cumulative GPA: 3.32 / 4.00
\end{detail}

\BigGap
{\textbf{Industrial Technical Institute Matria}},
Cairo, Egypt

\GapNoBreak
\BulletItem
Diploma of Associate Engineering (D.A.E) in Building and Construction
\hfill
\DatestampYMD{2009}{09}{16} --
\DatestampYMD{2011}{06}{28}
\begin{detail}
\SubBulletItem
General Grade: Excellent (24-Courses)
\SubBulletItem
Percentage: 95.77\%
\end{detail}



%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Research Experience}
{Research Experience}
{PDF:ResearchExperience}


\textbf{Spacecraft Systems Design},
Istanbul Technical University

\GapNoBreak
\BulletItem	
Undergraduate Research Student, Aerospace Engineering Department
\hfill
\DatestampYMD{2016}{2}{08} --
Present 
\begin{detail}
\SubBulletItem
Project:
Designing a Virtual Reality Cube-Sat.
\SubBulletItem
Supervisor:
Prof. Dr. Alim R\"ustem ASLAN
\SubBulletItem
Focus: System Engineering, Attitude Determination, Spacecraft Design.
\end{detail}


%%%%%%%%%%%%%
\href{https://www.linkedin.com/company/space-systems-technology-laboratory}
{\textbf{Space Systems Technology Laboratory (SSTL)}},
Cairo University
\GapNoBreak
\BulletItem	
Undergraduate Research Student, Aerospace Engineering Department
\hfill
\DatestampYMD{2012}{12}{15} --
\DatestampYMD{2014}{07}{15}
\begin{detail}
\SubBulletItem
Project: Control \& Design of Can-SAT, ROVER, Quad-copter, Rocket.
\SubBulletItem
Supervisors:
Prof. Dr. Mohammed Khalil Ibrahim
\SubBulletItem
Focus:
Can-Satellite, Quad-copter, ROVER, Rocket, Embedded Systems.
\end{detail}

%%%%%%%%%%%%%%%%
\href{http://aer.eng.cu.edu.eg/resources/aeronautical-systems-technology-laboratory/}
{\textbf{Aeronautical System Technology Lab (ASTL)}},
Cairo University
\GapNoBreak
\BulletItem	
Summer Intern, Aerospace Engineering Department
\hfill
\DatestampYMD{2013}{06}{15} --
\DatestampYMD{2013}{09}{15}
\begin{detail}
\SubBulletItem
Project:
Additive Manufacturing Trends in Aerospace and RC Flight Training
\SubBulletItem
Focus: RC Flight Training, CNC Machine, Laser Cutting Machine, Composite Forming Techniques.
\end{detail}

%%%%%%%%%%%%%
\href{http://udc2012.wix.com/udc}
{\textbf{Unmanned Aerial Systems Development Center (UDC)}},
Cairo University
\GapNoBreak
\BulletItem	
Student Participant, Aerospace Engineering Department
\hfill
\DatestampYMD{2012}{11}{15} --
\DatestampYMD{2013}{04}{15}
\begin{detail}
\SubBulletItem
Project:
Fabrication \& Flight Testing of an RC Aircraft
\SubBulletItem
Focus:
A simulated Remote Control, RC Aircraft.
\end{detail}



%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

%\section
%{Projects}
%{Projects}
%{PDF:Projects}



%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Awards \&\newline
Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}

\BulletItem
Erasmus+ Scholarship,
Istanbul Technical University
\hfill
\DatestampYMD{2015}{09}{25} --
\DatestampYMD{2016}{02}{05}
\begin{detail}
\SubItem
For attaining a high GPA \& English language exam.
\end{detail}

\Gap
\BulletItem
Participation of University Rover Challenge 2014,
Ranked 9th, Mars Society, USA
\hfill
\DatestampYMD{2014}{05}{10}

\begin{detail}
\SubItem
Design and build the next generation of Mars rovers that will one day work alongside human space exploration.
\end{detail}

\Gap
\BulletItem
Third Iran Cansat Competition, Ranked 7th
\hfill
\DatestampY{2013}
\newline
Astronautics Research Institute of the Iranian Space Research Center, Iran
\begin{detail}
\SubItem
Atmospheric Sounding Mission Category. 
\end{detail}

\Gap
\BulletItem
Certificate of Appreciation, American University in Cairo, Egypt
\hfill
\DatestampY{2012}
\begin{detail}
\SubItem
For the Distinguished Efforts in the Third Annual Cairo Science Festival. 
\end{detail}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL AFFILIATIONS & ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Professional Affiliations\newline
\& Activities}
{Professional Affiliations \& Activities}
{PDF:ProfessionalAffiliationsActivities}

\href{https://www.aiaa.org/}
{\textbf{The American Institute of Aeronautics and Astronautics (AIAA)}}
\GapNoBreak
\BulletItem
Member
\hfill
\DatestampY{2015} --
Present

\Gap
\href{http://www.spacegeneration.org/}
{\textbf{The Space Generation Advisory Council (SGAC)}}
\GapNoBreak
\BulletItem
Member
\hfill
\DatestampY{2015} --
Present

\Gap
\href{https://www.facebook.com/The-Astronomical-Society-of-Mahmoud-Mosque-ASMM-217726498294228/}
{\textbf{The Astronomical Society of Mahmoud Mosque (ASMM)}}, Giza, Egypt
\GapNoBreak
\BulletItem
Member
\hfill
\DatestampY{2009} --
\DatestampY{2015}

%%%%%%%%%%%%%%%%%%%%%%%
%% CAMPUS ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%

\section
{Campus Activities}
{Campus Activities}
{PDF:CampusActivities}

%%%%%%%%%%%%%

\href{https://www.facebook.com/iturokettakimi}
{\textbf{{\.I}T{\"{U}} Rocket Team}},
Istanbul Technical University

\GapNoBreak
\BulletItem	
Undergraduate Research Student, Aerospace Engineering Department
\hfill
\DatestampYMD{2016}{2}{15} --
Present 
\begin{detail}
\SubBulletItem
Project:
Designing a Solid Rocket for the Intercollegiate Engineering Competition.
\SubBulletItem
Focus: Rocket, Design, Control Unit.
\end{detail}

\href{http://schools.aucegypt.edu/news/aucinthenews/Pages/3rdScienceFestival.aspx}
{\textbf{Science Communication}},
American University in Cairo, Egypt

\GapNoBreak
\BulletItem
Volunteer 
\hfill
\DatestampYMD{2011}{11}{15} --
\DatestampYMD{2012}{08}{15}
\begin{detail}
\SubBulletItem
Participate in events such as Family Science, Star Gazing, Cairo Science Festival.
\end{detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Other Work\newline
Experience}
{Other Work Experience}
{PDF:OtherWorkExperience}

\href{https://www.facebook.com/kvectorfoundation}
{\textbf{K vector Foundation}},
Cairo university, Egypt

\GapNoBreak
\BulletItem
CEO,
Academic Division Head
\hfill
\DatestampYMD{2011}{12}{15} --
\DatestampYMD{2012}{08}{15}
\begin{detail}
\SubBulletItem
The aim to build a total Egyptian car\textquotesingle s factory.
\SubBulletItem
Providing workshops for engineering students to polish their experience.
\end{detail}

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\section
{Languages}
{Languages}
{PDF:Languages}

\BulletItem
Arabic: Native language.

\GapNoBreak
\BulletItem
English: Fluent (speaking, reading, writing).

\GapNoBreak
\BulletItem
Turkish: Intermediate (reading); basic (speaking, writing).

%%%%%%%%%%%%%%%%%%%%%
%% COMPUTER SKILLS %%
%%%%%%%%%%%%%%%%%%%%%

\section
{Computer skills}
{Computer skills}
{PDF:Computer Skills}
\BulletItem
Programming

\quad
\begin{tabular}{l l l l}
Matlab: Proficient & C/C++: Intermediate & LabVIEW: Basic & Mathematica: Basic\\
C\#: Basic & Python: Basic & µC Programming: Basic\\
\end{tabular}

\BulletItem
Web design

\quad
\begin{tabular}{l l l l}
HTML: Intermediate & Adobe Dreamweaver: Intermediate
\end{tabular}

\BulletItem
Finite element  analysis

\quad
\begin{tabular}{l l l l}
ANSYS Mechanical APDL
\end{tabular}
\BulletItem
Aerospace

\quad
\begin{tabular}{l l l l}
{Basic knowledge of XFOIL, Java Astrodynamics Toolkit, Systems Tool Kit (STK)}
\end{tabular}

\BulletItem
Software

\quad
\begin{tabular}{l l l l l l l}
{\TeX} & {\XeLaTeX} & Microsoft Office & Adobe Photoshop & Adobe Acrobat Pro\\ 
AutoCAD & SolidWorks & CATIA & Adobe Illustrator & CorelDRAW\\
\end{tabular}

\BulletItem
Operating system

\quad
\begin{tabular}{l l l l}
Linux: Ubuntu \& Mint & Windows: 10
\end{tabular}

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section
{Skills}
{Skills}
{PDF:Skills}
Self-learning (Software Defined Radio, Designing PCBs, SMD soldering), Teamwork, Management, Creativity, Critical Thinking, Work Hard Under Pressure, Analytical Thinking, Flexibility. 

%%%%%%%%%%%%%%%%%%%%%%%%
%% Research INTERESTS %%
%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Research Interests}
{Research Interests}
{PDF:Research Interests}

System Engineering,
Control Engineering,
Spacecraft Design,
Fluid Mechanics,
Robotics and Control,
Signal Processing.


%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\section
{Interests}
{Interests}
{PDF:Interests}

Amateur Astronomy,
Amateur Radio, 
Digital photography,
Radio Astronomy,
swimming.

%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%

\section
{References}
{References}
{PDF:References}

\BulletItem
\href{http://www.faa.itu.edu.tr/Icerik.aspx?sid=4688}
{\textbf{Prof. Dr. Alim R\"ustem ASLAN}}
\newline
Professor \& Head of Space Systems Design and Test Laboratory
\newline
Istanbul Technical University
\newline
Faculty of Aeronautics and Astronautics, ISTANBUL 34469, Turkey
\newline
\href{mailto:aslanr@itu.edu.tr}
{aslanr@itu.edu.tr}
\,\SubBulletSymbol\,
+90\,212\,285 7189/136

\BigGap
\BulletItem
\href{http://scholar.cu.edu.eg/?q=mkhalil/}
{\textbf{Prof. Dr. Mohammed Khalil Ibrahim}}
\newline
Professor \& Head of Aerodynamics Group
\newline
Cairo University
\newline
Faculty of Engineering, Aerospace Engineering Dept., Cairo University, Giza 12613, Egypt
\newline
\href{mailto:mkhalil@cu.edu.eg}
{mkhalil@cu.edu.eg}
\,\SubBulletSymbol\,
+966\,56\,308 5093 
\end{body}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SECTION WITH USAGE EXAMPLES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Change the date format option passed to the document class to adjust how dates are displayed throughout the document:
% MMMyyyy (``Dec~2010''),
% ddMMMyyyy (``31~Dec~2010''),
% MMMMyyyy (``December~2010''),
% ddMMMMyyyy (``31~December~2010''),
% yyyyMMdd (``2010-12-31''),
% yyyyMM (``2010-12''),
% yyyy (``2010'').


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MULTILINGUAL UNICODE EXAMPLES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\UseNoteFont% \null
\hfill%
[\textit{\CVNote}]%
%\hspace{2.0mm}\null
\end{document}